An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/4.xpg.tex
capitalize Section titles
add labels to sections
small fixes

\section{Tupling and lazy updates: xpg}
\subsection{Tupling: pg}

@@

\subsection{Lazy update: cpg}

@@

% If $ks_0$ is an identity function, $ks_1 \ s_2 = [100,2,3] :: [2,3]$. This is an unexpected result when we target it to be the updated source. If $ks_0 = \lambda \_.s$ where $s = [[1,2,3], [\,], [4,5]]$, the result will be what we want to see.$ks_1 \ s_2 = [100,2,3] :: [[\,], [4,5]] = [[100,2,3], [\,], [4,5]]$. Through the above example, using the continuation $ks$ as a constant function at the beginning contributes to retain the discarded things in the source.

\subsection{Lazy computation: kpg}

@@

Except $\kpginline{Skip}$ and $\kpginline{Case}$ where $s$ and $v$ hold actual values, functions for the computation will be kept in $ks'$ and $kv'$. When evaluating $\kpginline{bx_1 \circ bx_2}$, $ks_1'$ and $s_1$ in the result of the first assignment are still redundant but they are not evaluated. In $\kpginline{bx_1 \times bx_2}$, the evaluation of $ks'$ and $kv'$ will be done independently in two assignments using $\kpginline{bx_1}$ and $\kpginline{bx_2}$. There may be same computations in $fst \circ ks'$ and $snd \circ ks'$ as well as $fst \circ kv'$ and $snd \circ kv'$. It is possible to evaluate actual values in $s$ and $v$ before calling $\kpginline{bx_1}$ to remove the redundancy like that. One more thing, in $\kpginline{Case}$, we need to evaluate $ks' \ s'$ and $kv' \ v'$ to check the fi condition before returning the 6-tuple. Such evaluations can be done lazily to make programs run faster. We use the above small optimizations in our implementation.

>>>>

\section{Tupling and Lazy Updates: xpg} \label{sect:xpg}
\subsection{Tupling: pg}

@@

\subsection{Lazy Update: cpg}

@@

% If $ks_0$ is an identity function, $ks_1 \ s_2 = [100,2,3] :: [2,3]$. This is an unexpected result when we target it to be the updated source. If $ks_0 = \lambda \_.s$ where $s = [[1,2,3], [\,], [4,5]]$, the result will be what we want to see. $ks_1 \ s_2 = [100,2,3] :: [[\,], [4,5]] = [[100,2,3], [\,], [4,5]]$. Through the above example, using the continuation $ks$ as a constant function at the beginning contributes to retain the discarded things in the source.

\subsection{Lazy Computation: kpg}

@@

Except $\kpginline{Skip}$ and $\kpginline{Case}$ where $s$ and $v$ hold actual values, functions for the computation will be kept in $ks'$ and $kv'$. When evaluating $\kpginline{bx_1 \circ bx_2}$, $ks_1'$ and $s_1$ in the result of the first assignment are still redundant but they are not evaluated. In $\kpginline{bx_1 \times bx_2}$, the evaluation of $ks'$ and $kv'$ will be done independently in two assignments using $\kpginline{bx_1}$ and $\kpginline{bx_2}$. There may be same computations in $fst \circ ks'$ and $snd \circ ks'$ as well as $fst \circ kv'$ and $snd \circ kv'$. It is possible to evaluate actual values in $s$ and $v$ before calling $\kpginline{bx_1}$ to remove the redundancy like that. One more thing, in $\kpginline{Case}$, we need to evaluate $ks' \ s'$ and $kv' \ v'$ to check the $fi$ condition before returning the 6-tuple. Such evaluations can be done lazily to make programs run faster. We use the above small optimizations in our implementation.
